\documentclass[../the-millions-of-gestures.tex]{subfiles}
\begin{document}

\chapter{Finding a Place}
\TOWRITE


\section{Accidental location}

Let's begin with an analogy.

Why are you friends with the people you're friends with? At first blush it seems
like a silly question, but there's some meat behind it. If you're like most
people (myself included!), the people you've chosen to be friends with are
mostly accidental. Usually, they're people who were in close physical proximity
to you -- maybe coworkers, neighbors, friends of friends, etc -- people whom you
saw often enough to become familiar with. And, all else being equal, these were
people you didn't dislike enough to disassociate with.

As it happens, this is usually enough. If you spend enough time with someone you
don't hate, eventually you'll become friends. Maybe not "best friends", but
someone you'd feel obligated to talk to if you ran into on the street. Someone
you wouldn't mind going out for beers with once in a while. Someone you might
call up to do something if you were feeling bored.

Of course, there are notable exceptions. You have best friends and significant
others, and generally these are people that either you or they put "more effort"
into making happen. Maybe you met, decided you liked their style, and made a
move. From my own experience, my best relationships have been those where I've
identified an acquaintance whom I really like "on paper", and have decided to
tell them that I think they're super cool and I'd love to become better friends.
Often times it doesn't go anywhere, but when it does, it's truly something
marvelous.

\todo{proximity friends get the job done, but they're not satisfying. happiness
without joy}

There's something to be said about this. If you accept my premise, the
difference between best friends -- those people you'd go out of your way to
spend time with -- and your everyday acquaintance-friend is the degree to which
you and this other person decided to make it happen. For one reason or another,
you saw enough in the other that the investment into becoming great friends
seemed worthwhile.


I don't really want to talk about friends. I want to talk about finding a space
for yourself in this world. Not in a metaphorical sense, but like,
geographically.

The friends you made due to being in proximity with them are fine. They get the
job done. But, for the most part, you're friends by accident. In the same way,
the place you currently live is probably incidental as well. Maybe you were born
there, maybe you moved there for a job, or for a relationship. But most of the
time, for most of the people, they're not living somewhere because they sat down
and decided it would be the best place for them to live.

That's kind of insane, if you think about it.

\section{Cities have character}
\TOWRITE

\section{Move often}
\section{Figure out where to be}


\end{document}
